RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-04 review/response.tex

	\point Technical aspects: RIScatter is able to balance rate of primary transmission with rate of backscattered tags in a unified, user-controlled way, which brings technical advantages over existing approaches. This reviewer wonders why the authors only considered perfect CSI and did not assessed the impact of imperfect CSI on information rates (not the region!) given the limitations of tags and devices. Moreover, this reviewer is also sceptical about the assumption of perfect synchronization between the tags and the source. Can you explain why this is reasonable?
	\reply {Please kindly refer to response 2.1 for the discussion on imperfect CSI and response 2.2 for the discussion on perfect synchronization.}

	\point Simulation results: the authors opted for showing the results in terms of rate regions for several existing schemes and the proposed RISscatter. This is not properly motivated. Could explain why not include results such as information rates versus SNR or BER versus SNR?
	\reply {Thank you for the suggestion. In the previous version of the manuscript, we showed the impact of average noise power and disk radius on the achievable rate region. The former influences both primary and backscatter SNR, while the latter implicitly influences the backscatter SNR. In the revised manuscript, we have added explicit results on the achievable region vs primary SNR and backscatter SNR. However, we do not include BER vs SNR because (1) we have reached the page limit and (2) the BER performance is not the focus of this paper. We appreciate your understanding in this matter.}
